%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\definecolor{links}{HTML}{006400}
\usepackage{color}
%\hypersetup{colorlinks=true,urlcolor=links}
\hypersetup{colorlinks=true, urlcolor=links,pdfborderstyle={/S/U/W 1},pdfborder=0 0 1}
%\hypersetup{%
%  colorlinks=true,% hyperlinks will be coloured
%  linkcolor=green,% hyperlink text will be green
%  linkbordercolor=red,% hyperlink border will be red
%}

%\makeatletter
%\Hy@AtBeginDocument{%
%  \def\@pdfborder{0 0 1}% Overrides border definition set with colorlinks=true
%  \def\@pdfborderstyle{/S/U/W 1}% Overrides border style set with colorlinks=true
                                % Hyperlink border style will be underline of width 1pt
%}
%\makeatother

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{.6\textwidth}
{\Huge Fenimore {\textbf{Love}}}\\
\href{mailto:fenimoreplove@gmail.com}{fenimoreplove@gmail.com} \textbullet{} 571-314-7727\\
\end{minipage}
\hfill
\begin{minipage}[t]{.3\textwidth}
Portfolio: \underline{\href{https://polypmer.github.io}{polypmer.github.io}}\\
Github: \href{https://github.com/polypmer}{@polypmer}
\end{minipage}
\namesection{}{} % for some reason...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Ghess}
\descript{| golang chess engine and ai}
\href{https://ghess-chess.herokuapp.com/}{A chess engine in Go; it supports PGN and includes a Websocket GUI and a fast and effective AI.}
\sectionsep

\runsubsection{Democracy Droid!}
\descript{| java android app for media streaming}
\href{https://play.google.com/store/apps/details?id=com.workingagenda.democracydroid}{A Democracy Now! Android App for streaming and downloading podcasts. It is a popular application with around 1,000 active users around the world.}
\sectionsep

\runsubsection{the treasure map}
\descript{| python free stuff mapper}
\href{http://treasure.plyp.org}{ Flask Application which scrapes and geolocates free stuff.}
\sectionsep

\runsubsection{Wink}
\descript{| php flat file photo gallery}
\href{http://wink.plyp.org}{A PHP flat file photo gallery, with Bootstrap, REST endpoints, and authentication.}
\sectionsep

\runsubsection{Muse}
\descript{| django social network}
\href{http://realmess.plyp.org/}{A Django social network which encourages and tracks creative production.}
\sectionsep

\runsubsection{Fissure}
\descript{| java android app for gifs}
\href{https://github.com/polypmer/fissure-android}{An Android app for generating and viewing GIFs; it is popular in the open source community (F-Droid) and translated into French and Japanese.}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Recurse Center}
\descript{| participant }
\location{September 2016 – Present \textbullet{}  New York, NY}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Implemented a chess AI and websocket client in Go
\item Built a PostgreSQL database and JSON API for an Android App that puts reddit-style comments onto a map in Go
\item Implemented the BitTorrent protocol for distributed file-sharing in a command line client in Go
\end{tightemize}
\sectionsep

\runsubsection{Ecole élémentaire Bruxelles}
\descript{| programming teaching assistant }
\location{January 2016 – July 2016 \textbullet{}  Paris, France}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Taught video game development using Scratch
\item Worked through fundamental concepts such as loops, conditionals, two dimensional planes, and threading
\end{tightemize}
\sectionsep

\runsubsection{Knowledge Ecology International}
\descript{| developer }
\location{January 2016}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Published an Android app for a non-profit organization, Knowledge Ecology International
\item Worked with Twitter and Youtube API to aggregate their data
\end{tightemize}
\sectionsep


\runsubsection{McGill Digital Humanities Project}
\descript{| researcher }
\location{January 2015 – July 2015 \textbullet{}  Montreal, QC}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Used Python, NTLK, and Regex to analyze a large corpus of text from early modern England
\item Developed and tested a hypothesis on criminality and secularity in early literary practice
\end{tightemize}
\sectionsep

\section{Languages}
\subsection{Go, Python, Java, PHP} 
Django, Flask, Bootstrap, libGDX, Arduino \textbullet{} MySQL, PostgreSQL, BoltDB
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\runsubsection{McGill University}
\descript{| Master in Religious Studies}
\location{September 2013 - July 2015 \textbullet{} Montreal, QC}
The Work of Text in the Age of Digital Reproduction:
\textit{A comparison of Ancient Literary Practice and the Copy Left Movement}

\runsubsection{McGill University}
\descript{| Bachelor in Religious Studies}
\location{September 2009 - July 2013 \textbullet{} Montreal, QC}
Focus on exegesis of classical texts (Latin and Greek) and the philosophy of religion.
\sectionsep



\end{document}  \documentclass[]{article}
